Quantitative Comparison With Experiments Reveals Imperfections in Force Fields' Descriptions of Phospholipid--Cholesterol Interactions

### 2023-05-18 MANUSCRIPT/manuscript.tex
Update manuscript.tex

\begin{abstract}
Cholesterol is a central building block in biomembranes, where it induces orientational order, slows down diffusion, renders the membrane stiffer, and drives domain formation. Molecular dynamics simulations have played a crucial role in resolving these effects at molecular level, yet it has recently become evident that different simulation force fields predict quantitatively different behavior. Although easily neglected, identifying such limitations are becoming increasingly important as the field rapidly progresses towards simulations of complex membranes mimicking the \textit{in vivo} conditions where it is crucial to accurately model the interactions between the fundamental building blocks of biomembranes, such as phospholipids and cholesterol.
%
Here, we define quantitative quality measures for binary lipid mixtures in membranes against C--H bond order parameters and lateral diffusion coefficients from NMR as well as form factors from X-ray scattering. Based on these measures, we then perform a systematic evaluation on the ability of commonly used force fields to describe the structure and dynamics of binary mixtures of phosphatidylcholine and cholesterol. None of the tested force fields clearly outperforms the others across the tested properties and conditions, yet Slipids parameters provide the best overall performance.
%
The quality evaluation metrics introduced in this work will particularly foster the future force field development and refinement for multi-component membranes with automated approaches.
\end{abstract}

@@

Cellular membranes contain an incredibly complex mixture of lipid molecules \cite{lorent2020plasma} which are unevenly distributed in the membrane plane and across its leaflets \cite{van2008membrane,wang2020membrane,kinnun2020lateral}. A key player driving the lateral heterogeneity is cholesterol (CHOL), which is present at concentrations between $\sim$10~mol-\% (endoplasmic reticulum) and up to $\sim$50~mol-\% (plasma membrane) \cite{van2008membrane}. CHOL has the unique ability to order neighbouring lipids and thus induce the liquid ordered (L\textsubscript{o}) phase in model membranes \cite{mouritsen2004s,ipsen87,kinnunen91,rog2009ordering}. In the cellular setting, the interaction between other lipids and CHOL is associated with the formation of lipid rafts and nanodomains \cite{Simons97,cebecauer2018membrane}. This heterogeneity can then further regulate protein distribution \cite{milovanovic2015hydrophobic} or conformation \cite{kelkar2007modulation}, in addition to the direct modulation of protein function \cite{gimpl2016interaction,guixa2017membrane,manna2016mechanism}.

@@

While simulations of complex membranes with CHOL have become relatively straightforward task, estimating the trustworthiness of MD simulations for complex membranes remains a challenge. Our earlier work has demonstrated that the conformational ensembles of lipids from an MD simulation can be evaluated against C--H bond order parameters from solid state NMR experiments \cite{botan15,ollila16,catte2016molecular,antila2019headgroup,bacle2021inverse}. This approach has been useful for finding the best force fields for the description of the headgroups of phosphatidylcholine (PC)~\cite{botan15}, phosphatidylserine (PS)~\cite{antila2019headgroup}, phoshatidylethanolamine (PE)~\cite{bacle2021inverse} and phosphatidylglycerol (PG)~lipids \cite{bacle2021inverse}, for evaluating and improving membrane interactions with ions~\cite{catte2016molecular,antila2019headgroup,bacle2021inverse,melcr18,melcr19} and small molecules~\cite{nencini22}, and for finding simulation parameters predicting most realistic packing properties of membranes~\cite{antila2022emerging,NMRlipidsDatabank}. Furthermore, quantitative quality measures based on C--H bond order parameters have been recently defined and used to rank simulations in the NMRlipids databank~\cite{NMRlipidsDatabank}. However, such automatic quality evaluation is limited to simulations for which experimental data at a corresponding composition and temperature are available. Because simulations mimicking all experimental compositions for multi-component membranes are often tedious to produce, quality evaluation of mixed lipid bilayers is not yet fully automatized in the NMRlipids databank.

@@

To simplify the interpolation of order parameter data to intermediate CHOL concentrations (see \textit{``Quantitative quality evaluation of the effect of CHOL on membrane properties''} below), C--H bond order parameters of 2 (3) hydrogens in CH$_2$ (CH$_3$) groups in the POPC acyl chains were averaged. These groups rotate freely and thus the order parameters are essentially identical for both (all) hydrogens in experiments and simulations. An exception to this are the hydrogens bound to the 2\textsuperscript{nd} carbon in the oleate chain; they lack rotational averaging in both simulations and experiments, and were thus treated separately in our analyses. The C--H order parameters for the POPC head group are shown separately for all CH$_2$ groups, \textit{i.e.} no averaging was performed.

@@

\paragraph{Quantitative quality evaluation of the effect of CHOL on membrane properties:} To ease the evaluation of simulations against experimental data with non-matching CHOL concentrations, we interpolated the effect of CHOL in simulations and experiments for CHOL concentrations ranging from 0\% to 46\%. 2D matrices were created by interpolation for the oleate and palmitate chain order parameters (as a function of carbon atoms in the acyl chains and CHOL concentration) using the \texttt{interp2} function in Matlab based on linear interpolation. Similar matrices were also generated for the electron density profiles (as a function of normal distance from bilayer center and CHOL concentration) but with the \texttt{scatteredInterpolant} function in Matlab based on Delanuay triangulation \cite{amidror2002scattered}. Linear 1D interpolation with the \texttt{interp1} function in Matlab was used for the CHOL-dependence of the 1\textsuperscript{st} and 2\textsuperscript{nd} form factor minima locations and diffusion coefficients. These interpolations were then used to calculate deviations (in \%) from experimental values across CHOL concentrations to quantify the quality of the lipid force fields.  For the 2D matrices, the absolute values of the differences between matrices from simulations and experiments were first calculated. The averages of differences over the carbon atoms in the acyl chain (order parameters) or across the entire $z$ coordinate in the simulation (density profiles) were then calculated. This resulted in 1D deviation vectors as a function of CHOL concentration. For diffusion coefficients and form factor minima, the absolute value of the difference of the interpolated 1D vectors of simulation and experimental data was calculated to provide deviation as a function of CHOL concentration. All these 1D vectors were normalized by dividing them by the experimental values to provide relative deviations in \% between a simulation and experiments as a function of CHOL concentration. For C--H bond order parameters, also the deviation matrices between simulations and experiments were used to illustrate quality of simulations.

@@

CHOL is known to induce order in lipid membranes by increasing the fraction of \textit{anti} conformations in the acyl chains of phospholipids \cite{ferreira13}, which is suggested to play critical role in the phase behaviour of PC--CHOL mixtures \cite{ipsen87}. Consequently, the correct CHOL ordering effect is expected to be a necessary condition for a force field used to understand lipid--CHOL phase behaviour. CHOL ordering effect can be experimentally quantified by measuring the C--H bond order parameters using $^{13}$C or $^{2}$H NMR techniques, and the result can be also directly compared to MD simulations~\cite{ollila16}. Simulations generally reproduce the CHOL ordering effect, but order parameters often deviate from experiments at high CHOL concentrations~\cite{ferreira13,madej15}. Furthermore, it has not been clear how accurately different force field parameters capture the details of lipid--CHOL interactions and which force field would give most realistic results for simulations of complex mixtures where such interactions play critical roles.

@@

The effect of CHOL on structural properties of bilayers is compared between the SDP model (based on experimental form factors) and MD simulation results in Fig.~\ref{fig:densmaps}.  All force fields demonstrate increasing thickness upon addition of CHOL that saturates after approximately 30~mol-\% (bottom middle panel in Fig.~\ref{fig:densmaps}). MD simulations agree well with the SDP model below 30~mol-\% but overshoot the SDP results at high CHOL concentrations. Lipid17 simulations are exception as they predict thinner membranes than SDP model at low CHOL concentrations, and clear saturation of thickness increase is not observed, unlike for other force fields and experiments.

@@

For more detailed comparison of membrane structure, we interpolated the changes in electron density profiles along membrane normal (Fig.~\ref{SIfig:densprofs}) as a function of CHOL concentration to create two-dimensional electron density maps shown in Fig.~\ref{fig:densmaps}. Overall, all electron density profiles share the same features across all CHOL concentrations; a high-density band corresponding to the tightly-packed interfacial region containing electron-rich phosphorus, a low-density region at the core of the membrane occupied by the disordered acyl chains, and intermediate density in the rest of the lipid regions as well as the aqueous phase. However, a more detailed look at the profiles in Fig.~\ref{fig:densmaps} reveals differences between the force fields and SPD model. CHARMM36 has the sharpest low- and high-density bands among MD simulation results indicating smaller membrane fluctuations that would smear the bands, and the same is true for MacRog at higher CHOL concentrations. The less sharp bands for Lipid17 and especially Slipids profiles indicate that the membranes are more flexible with these force fields. SDP model gives the most sharp bands (bottom left panel in Fig.~\ref{fig:densmaps} and original electron density profiles in Fig.~\ref{SIfig:densprofs}), suggesting more uniform membrane structure than any MD simulation. However, System size plays a role here as  undulations smear out the density profile features with increasing simulation box size as demonstrated in Fig.~\ref{SIfig:densprofssize} by the density maps calculated for the CHARMM36 simulations in three sizes.  Still, even in the smallest system, the band intensities are less localized than in the SDP model. This difference might arise because most undulations are assigned to structure factor rather than form factor in their deconvolution, but it could also indicate different elastic properties between simulation and experiment.

@@

The lipid force fields again show significantly different behavior. Lipid17 and CHARMM36 show too fast dynamics for pure POPC, and the slow-down induced by CHOL is exaggerated as compared to experiment. Diffusion in MacRog is generally too slow, yet Slipids provides an essentially quantitative agreement with experiment across the studied CHOL concentrations, and thus significantly outperforms other force fields in terms of lateral dynamics. Interestingly, there is no correlation between dynamic and structural properties described earlier when it comes to the deviations from experiments. To investigate if the differences in lateral diffusion coefficients could be explained by different Lennard-Jones (LJ) cutoff values, we repeated simulations at 0~mol-\% and 47~mol-\% CHOL for Slipids using a shorter cutoff of 0.9~nm corresponding to that of Lipid17, while original cutoff for Slipids was 1.4~nm (see Table~\ref{SItab:params}). The PBC-corrected diffusion coefficient values with shorter cutoff, shown in the top panel of Fig.~\ref{fig:dynamics} as hollow red circles, are only slightly larger than the original values, indicating that the LJ cutoff alone does not explain the differences between force fields, but they truly spark from differences in the force field interaction parameters.

When comparing lipid lateral diffusion between simulations and experiments, it is important to note that the PBC correction does not only affect values of diffusion coefficients but also qualitatively changes their trends as a function of cholesterol. This results from the fact that the size of the PBC correction, Eq.~\eqref{eq:sdlatpbc}, depends on membrane viscosity, which further depends on CHOL concentration. For example, Fig.~\ref{SIfig:dvschol} shows that Lipid17 and CHARMM36 systemically underestimate the experimental values in systems with all sizes simulated here while the effect of CHOL seems to be qualitatively reproduced. However, the PBC corrected values significantly overshoot the experiment at low CHOL concentration, and CHOL induces a more drastic slowdown in simulations leading to values close to experimental ones at 47~mol-\% CHOL. With MacRog, also the PBC corrected values fall below the experimental ones, yet the slowdown effect of CHOL again seems stronger than in experiment. With Slipids, the CHOL-dependence seems too weak with finite system sizes, yet after accounting for PBC effects, the agreement with experiment is excellent. These results highlight that little can be said about CHOL-dependence of lateral diffusion coefficients without performing simulations with multiple box sizes required for the PBC correction at different CHOL concentrations. Therefore, fine-tuning of interaction parameters to correctly reproduce lateral diffusion coefficients can require massive number of simulations.

@@

Since the contributions from the form factor minima deviations are barely visible for some force fields in the leftmost columns of Fig.~\ref{fig:deviation}, we have highlighted the error in the 1\textsuperscript{st} minimum location in the top right panel of Fig.~\ref{fig:deviation}. This panel demonstrates that apart from CHARMM36, all force fields capture the location of the 1\textsuperscript{st} minimum relatively well at low CHOL concentrations, but deviate significantly at larger CHOL concentrations.

@@

The tested all-atom force fields captured the most important general effects of CHOL on membrane properties: increased acyl chain ordering, concomitant increase in bilayer thickness, and reduced lateral diffusion rate of lipids. However, quantitative comparison reveals differences between force fields and their qualities evaluated against NMR and X-ray scattering data. Comparison with NMR order parameters and X-ray scattering form factors propose that simulations reproduce experimental results up to 20~mol-\% of CHOL, but overestimate acyl chain ordering and membrane thickness after further addition of CHOL. An apparent exception to this is the Lipid17 force field, yet their seemingly better agreement with experiments can be explained by the over-correction of the originally underestimated acyl chain order at low CHOL concentrations upon CHOL addition. In conclusion, a unified picture emerging from comparison with NMR and X-ray scattering data suggests that all the tested force fields overestimate the CHOL ordering effect, particularly above 20~mol-\% of CHOL. Previously published comparison~\cite{ferreira13} suggests the same conclusion for historically relevant Berger/H{\"o}ltje force field parameters \cite{Berger97,Holtje01} that were not included in this work.

Besides the ordering effect, effect of CHOL on membrane properties has been discussed also in terms of the CHOL condensing effect which refers to a decrease in the \emph{area per phospholipid} upon the addition of CHOL (negative partial area) \cite{edholm2005areas}, or to CHOL having a diminishing partial area, meaning that a certain amount of CHOL could be added to a phospholipid bilayer without effecting its total area (zero partial area) \cite{javanainen2017two}. At the physiological CHOL concentrations in the range from 0 to 30~mol-\%, only MacRog predicts negative partial area for CHOL, while CHARMM36 predicts zero partial area, and Slipids and Lipid17 predict small positive partial areas. Considering that Slipids and Lipid17 perform best in our quality evaluation against experiments, yet still slightly overestimating the CHOL condensing effect, our results suggests that CHOL has a positive but small partial area.

>>>>

\begin{abstract}
Cholesterol is a central building block in biomembranes, where it induces orientational order, slows down diffusion, renders the membrane stiffer, and drives domain formation. Molecular dynamics simulations have played a crucial role in resolving these effects at molecular level, yet it has recently become evident that different simulation force fields predict quantitatively different behavior. Although easily neglected, identifying such limitations are becoming increasingly important as the field rapidly progresses towards simulations of complex membranes mimicking the \textit{in vivo} conditions where it is crucial to accurately model the interactions between the fundamental building blocks of biomembranes, such as phospholipids and cholesterol.
%
Here, we define quantitative quality measures for binary lipid mixtures in membranes against C--H bond order parameters and lateral diffusion coefficients from NMR as well as form factors from X-ray scattering. Based on these measures, we then perform a systematic evaluation on the ability of commonly used force fields to describe the structure and dynamics of binary mixtures of phosphatidylcholine and cholesterol. None of the tested force fields clearly outperforms the others across the tested properties and conditions but Slipids parameters provide the best overall performance.
%
The quality evaluation metrics introduced in this work will particularly foster the future force field development and refinement for multi-component membranes with automated approaches.
\end{abstract}

@@

Cellular membranes contain an incredibly complex mixture of lipid molecules \cite{lorent2020plasma} unevenly distributed in the membrane plane and across its leaflets \cite{van2008membrane,wang2020membrane,kinnun2020lateral}. A key player driving the lateral heterogeneity is cholesterol (CHOL), which is present at concentrations between $\sim$10~mol-\% (endoplasmic reticulum) and up to $\sim$50~mol-\% (plasma membrane, viral envelopes) \cite{van2008membrane}. CHOL has the unique ability to order neighbouring lipids and thus induce the liquid ordered (L\textsubscript{o}) phase in model membranes \cite{mouritsen2004s,ipsen87,kinnunen91,rog2009ordering}. In the cellular setting, the interaction between other lipids and CHOL is associated with the formation of lipid rafts and nanodomains \cite{Simons97,cebecauer2018membrane}. This heterogeneity can then further regulate protein distribution \cite{milovanovic2015hydrophobic} or conformation \cite{kelkar2007modulation}, in addition to the direct modulation of protein function \cite{gimpl2016interaction,guixa2017membrane,manna2016mechanism}.

@@

While simulations of complex membranes with CHOL have become relatively straightforward task, estimating the trustworthiness of MD simulations for membranes remains a challenge, especially as the number of components and complexity increase. Our earlier work has demonstrated that the conformational ensembles of lipids from an MD simulation can be evaluated against C--H bond order parameters from solid state NMR experiments \cite{botan15,ollila16,catte2016molecular,antila2019headgroup,bacle2021inverse}. This approach has been useful for finding the best force fields for the description of the headgroups of phosphatidylcholine (PC)~\cite{botan15}, phosphatidylserine (PS)~\cite{antila2019headgroup}, phoshatidylethanolamine (PE)~\cite{bacle2021inverse} and phosphatidylglycerol (PG)~lipids \cite{bacle2021inverse}, for evaluating and improving membrane interactions with ions~\cite{catte2016molecular,antila2019headgroup,bacle2021inverse,melcr18,melcr19} and small molecules~\cite{nencini22}, and for finding simulation parameters predicting most realistic packing properties of membranes~\cite{antila2022emerging,NMRlipidsDatabank}. Furthermore, quantitative quality measures based on C--H bond order parameters have been recently defined and used to rank simulations in the NMRlipids databank~\cite{NMRlipidsDatabank}. However, such automatic quality evaluation is limited to simulations for which experimental data at a corresponding composition and temperature are available. Because simulations mimicking all experimental compositions for multi-component membranes are often tedious to produce, quality evaluation of mixed lipid bilayers is not yet fully automatized in the NMRlipids databank.

@@

To simplify the interpolation of order parameter data to intermediate CHOL concentrations (see \textit{``Quantitative quality evaluation of the effect of CHOL on membrane properties''} below), C--H bond order parameters of 2 (3) hydrogens in CH$_2$ (CH$_3$) groups in the POPC acyl chains were averaged. These groups rotate freely and thus the order parameters are essentially identical for both (all) hydrogens in experiments and simulations. An exception to this are the hydrogens bound to the 2\textsuperscript{nd} carbon in the oleate chain; they lack rotational averaging in both simulations and experiments, and were thus treated separately in our analyses. The C--H order parameters for the POPC head group are shown separately for all CH$_2$ groups, \textit{i.e.}, no averaging was performed.

@@

\paragraph{Quantitative quality evaluation of the effect of CHOL on membrane properties:} To ease the evaluation of simulations against experimental data with non-matching CHOL concentrations, we interpolated the effect of CHOL in simulations and experiments for CHOL concentrations ranging from 0\% to 46\%. 2D matrices were created by interpolation for the oleate and palmitate chain order parameters (as a function of carbon atoms in the acyl chains and CHOL concentration) using the \texttt{interp2} function in Matlab based on linear interpolation. Similar matrices were also generated for the electron density profiles (as a function of normal distance from bilayer center and CHOL concentration) but with the \texttt{scatteredInterpolant} function in Matlab based on Delaunay triangulation \cite{amidror2002scattered}. Linear 1D interpolation with the \texttt{interp1} function in Matlab was used for the CHOL-dependence of the 1\textsuperscript{st} and 2\textsuperscript{nd} form factor minima locations and diffusion coefficients. These interpolations were then used to calculate deviations (in \%) from experimental values across CHOL concentrations to quantify the quality of the lipid force fields.  For the 2D matrices, the absolute values of the differences between matrices from simulations and experiments were first calculated. The averages of differences over the carbon atoms in the acyl chain (order parameters) or across the entire $z$ coordinate in the simulation (density profiles) were then calculated. This resulted in 1D deviation vectors as a function of CHOL concentration. For diffusion coefficients and form factor minima, the absolute value of the difference of the interpolated 1D vectors of simulation and experimental data was calculated to provide deviation as a function of CHOL concentration. All these 1D vectors were normalized by dividing them by the experimental values to provide relative deviations in \% between a simulation and experiments as a function of CHOL concentration. For C--H bond order parameters, the deviation matrices between simulations and experiments were also used to illustrate quality of simulations.

@@

CHOL is known to induce order in lipid membranes by increasing the fraction of \textit{anti} conformations in the acyl chains of phospholipids \cite{ferreira13}, which is suggested to play critical role in the phase behaviour of PC--CHOL mixtures \cite{ipsen87}. Consequently, the correct CHOL ordering effect is expected to be a necessary condition for a force field used to understand lipid--CHOL phase behaviour. CHOL ordering effect can be experimentally quantified by measuring the C--H bond order parameters using $^{13}$C or $^{2}$H NMR techniques, and the result can also be directly compared to MD simulations~\cite{ollila16}. Simulations generally reproduce the CHOL ordering effect, but order parameters often deviate from experiments at high CHOL concentrations~\cite{ferreira13,madej15}. Furthermore, it has not been clear how accurately different force field parameters capture the details of lipid--CHOL interactions and which force field would give most realistic results for simulations of complex mixtures where such interactions play critical roles.

@@

The effect of CHOL on structural properties of bilayers is compared between the SDP model (based on experimental form factors) and MD simulation results in Fig.~\ref{fig:densmaps}.  All force fields demonstrate increasing thickness upon addition of CHOL that saturates after approximately 30~mol-\% (bottom middle panel in Fig.~\ref{fig:densmaps}). MD simulations agree well with the SDP model below 30~mol-\% but overshoot the SDP results at high CHOL concentrations. Lipid17 simulations are the exception as they predict thinner membranes than SDP model at low CHOL concentrations, and clear saturation of thickness increase is not observed, unlike for other force fields and experiments.

@@

For more detailed comparison of membrane structure, we interpolated the changes in electron density profiles along membrane normal (Fig.~\ref{SIfig:densprofs}) as a function of CHOL concentration to create two-dimensional electron density maps shown in Fig.~\ref{fig:densmaps}. Overall, all electron density profiles share the same features across all CHOL concentrations; a high-density band corresponding to the tightly-packed interfacial region containing electron-rich phosphorus, a low-density region at the core of the membrane occupied by the disordered acyl chains, and intermediate density in the rest of the lipid regions as well as the aqueous phase. However, a more detailed look at the profiles in Fig.~\ref{fig:densmaps} reveals differences between the force fields and SPD model. CHARMM36 has the sharpest low- and high-density bands among MD simulation results indicating smaller membrane fluctuations that would smear the bands, and the same is true for MacRog at higher CHOL concentrations. The less sharp bands for Lipid17 and especially Slipids profiles indicate that the membranes are more flexible with these force fields. SDP model gives the most sharp bands (bottom left panel in Fig.~\ref{fig:densmaps} and original electron density profiles in Fig.~\ref{SIfig:densprofs}), suggesting more uniform membrane structure than any MD simulation. However, system size plays a role here as  undulations smear out the density profile features with increasing simulation box size as demonstrated in Fig.~\ref{SIfig:densprofssize} by the density maps calculated for the CHARMM36 simulations in three sizes.  Still, even in the smallest system, the band intensities are less localized than in the SDP model. This difference might arise because most undulations are assigned to structure factor rather than form factor in their deconvolution, but it could also indicate different elastic properties between simulation and experiment.

@@

The lipid force fields again show significantly different behavior. Lipid17 and CHARMM36 show too fast dynamics for pure POPC, and the slow-down induced by CHOL is exaggerated as compared to experiment. Diffusion in MacRog is generally too slow, yet Slipids provides an essentially quantitative agreement with experiment across the studied CHOL concentrations, and thus significantly outperforms other force fields in terms of lateral dynamics. Interestingly, there is no correlation between dynamic and structural properties described earlier when it comes to the deviations from experiments. To investigate if the differences in lateral diffusion coefficients could be explained by different Lennard-Jones (LJ) cutoff values, we repeated simulations at 0~mol-\% and 47~mol-\% CHOL for Slipids using a shorter cutoff of 0.9~nm corresponding to that of Lipid17, while original cutoff for Slipids was 1.4~nm (see Table~\ref{SItab:params}). The PBC-corrected diffusion coefficient values with shorter cutoff, shown in the top panel of Fig.~\ref{fig:dynamics} as hollow red circles, are only slightly larger than the original values, indicating that differences arise from a combination of force field interaction parameters and are not explained by the LJ cutoff alone.

When comparing lipid lateral diffusion between simulations and experiments, it is important to note that the PBC correction does not only affect values of diffusion coefficients but also qualitatively changes their trends as a function of cholesterol. This results from the fact that the size of the PBC correction, Eq.~\eqref{eq:sdlatpbc}, depends on membrane viscosity, which further depends on CHOL concentration. For example, Fig.~\ref{SIfig:dvschol} shows that Lipid17 and CHARMM36 systemically underestimate the experimental values in systems with all sizes simulated here while the effect of CHOL seems to be qualitatively reproduced. However, the PBC corrected values significantly overshoot the experiment at low CHOL concentration, and CHOL induces a more drastic slowdown in simulations, leading to values close to experimental ones at 47~mol-\% CHOL. With MacRog, also the PBC corrected values fall below the experimental ones, yet the slowdown effect of CHOL again appears stronger than in experiment. With Slipids, the CHOL-dependence seems too weak with finite system sizes, yet after accounting for PBC effects, the agreement with experiment is excellent. These results highlight that little can be said about CHOL-dependence of lateral diffusion coefficients without performing simulations with multiple box sizes required for the PBC correction at different CHOL concentrations. Therefore, fine-tuning of interaction parameters to correctly reproduce lateral diffusion coefficients can require massive number of simulations.

@@

Since the contributions from the form factor minima deviations barely are visible for some force fields in the leftmost columns of Fig.~\ref{fig:deviation}, we have highlighted the error in the 1\textsuperscript{st} minimum location in the top right panel of Fig.~\ref{fig:deviation}. This panel demonstrates that apart from CHARMM36, all force fields capture the location of the 1\textsuperscript{st} minimum relatively well at low CHOL concentrations, but deviate significantly at larger CHOL concentrations.

@@

The tested all-atom force fields captured the most important general effects of CHOL on membrane properties: increased acyl chain ordering, concomitant increase in bilayer thickness, and reduced lateral diffusion rate of lipids. However, quantitative comparison reveals differences between force fields and their qualities evaluated against NMR and X-ray scattering data. Comparison with NMR order parameters and X-ray scattering form factors propose that simulations reproduce experimental results up to 20~mol-\% of CHOL, but overestimate acyl chain ordering and membrane thickness after further addition of CHOL. An apparent exception to this is the Lipid17 force field, yet its seemingly better agreement with experiments can be explained by the over-correction of the originally underestimated acyl chain order at low CHOL concentrations upon CHOL addition. In conclusion, a unified picture emerging from comparison with NMR and X-ray scattering data suggests that all the tested force fields overestimate the CHOL ordering effect, particularly above 20~mol-\% of CHOL. Previously published comparison~\cite{ferreira13} suggests the same conclusion for historically relevant Berger/H{\"o}ltje force field parameters \cite{Berger97,Holtje01} that were not included in this work.

Besides the CHOL-induced ordering, effects on membrane properties has been discussed also in terms of the CHOL condensing effect which refers to a decrease in the \emph{area per phospholipid} upon the addition of CHOL (negative partial area) \cite{edholm2005areas}, or to CHOL having a diminishing partial area, meaning that a certain amount of CHOL could be added to a phospholipid bilayer without effecting its total area (zero partial area) \cite{javanainen2017two}. At the physiological CHOL concentrations in the range from 0 to 30~mol-\%, only MacRog predicts negative partial area for CHOL, while CHARMM36 predicts zero partial area, and Slipids and Lipid17 predict small positive partial areas. Considering that Slipids and Lipid17 perform best in our quality evaluation against experiments, yet still slightly overestimating the CHOL condensing effect, our results suggest that CHOL has a positive but small partial area.
